The effect of climate forcing on numerical simulations of the Cordilleran Ice Sheet at the Last Glacial Maximum

### 2013-11-19 cordillera-climate.tex
General footnotes clear-up
Final comments from Arjen
Add acknowledgements

% To-do footnotes
\newcommand{\needref}[0]{\footnote{Reference needed}}
\newcommand{\julien}[1]{\footnote{\textbf{Julien:} #1}}
\newcommand{\arjen}[1]{\footnote{\textbf{Arjen:} #1}}
\newcommand{\qiong}[1]{\footnote{\textbf{Qiong:} #1}}
\newcommand{\irina}[1]{\footnote{\textbf{Irina:} #1}}

@@

% Authors
\author[1]{Julien Seguinot}
\author[2]{Constantine Khroulev}
\author[3]{Irina Rogozhina}
\author[1]{Arjen Stroeven}
\author[1]{Qiong Zhang}
\runningauthor{J. Seguinot et al.}
\correspondence{J. Seguinot\\ (julien.seguinot@natgeo.su.se)}

@@

% Acknowledgements
%\begin{acknowledgements}
%\end{acknowledgements}

>>>>

@@

% Authors
\author[1]{Julien Seguinot}
\author[2]{Constantine Khroulev}
\author[3]{Irina Rogozhina}
\author[1]{Arjen P. Stroeven}
\author[1]{Qiong Zhang}
\runningauthor{J. Seguinot et al.}
\correspondence{J. Seguinot\\ (julien.seguinot@natgeo.su.se)}

@@

% Acknowledgements
\begin{acknowledgements}
We thank Ed Bueler and Andy Aschwanden for providing constant support on PISM and patiently answering our questions on the code internals, Laurent Brodeau and Soon-Heum Ko for assistance concerning software installations on supercomputing resources, and all PISM authors for providing the model open-source. Funding was provided by the Swedish Research Council (VR) to A. Stroeven (No. 2008-3449) and Stockholm University. Computer resources were provided by the Swedish National Infrastructure for Computing (SNIC) at the National Supercomputing Center (NSC) to A. Stroeven (No. 2013/1-145).

% Author contributions
\textit{Author contributions.}
J. Seguinot ran the simulations and wrote most of the paper; C. Khroulev implemented necessary code changes in PISM; I. Rogozhina helped with model set-up and experiment design; A. Stroeven initiated the Cordilleran Ice Sheet modelling project; and Q. Zhang prepared some of the forcing data. All authors contributed to the redaction.
\end{acknowledgements}
